---
title: "Homework 6 solutions"
author: "Yali Zhai"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```




### Problem 2

Load and clean data.

```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace)
  )
```


I guess the mother’s weight at delivery is positively associated with baby's birth weight. Fit a simple linear regression.

```{r}
model_fit = lm(bwt ~ delwt, data = baby_df)
```



residuals v.s fitted values plot

```{r}
baby_df %>% 
  add_predictions(model_fit) %>% 
  add_residuals(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()

```



cross validation

```{r}
cv_df =
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(
    model_fit  = map(train, ~lm(bwt ~ delwt, data = .x)),
    model_alter1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_alter2  = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x))) %>%
  mutate(
    rmse_fit = map2_dbl(model_fit, test, ~rmse(model = .x, data = .y)),
    rmse_alter1 = map2_dbl(model_alter1, test, ~rmse(model = .x, data = .y)),
    rmse_alter2 = map2_dbl(model_alter2, test, ~rmse(model = .x, data = .y)))
```



comparison of distribution of rmse

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```




### Problem 3

load data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


bootstrap

```{r}
bootstrap_results =
 weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    summary = map(models, broom::glance),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) 

```


distribution of r_squared

```{r}
bootstrap_results %>% 
  unnest(summary) %>% 
   ggplot(aes(x = r.squared)) + geom_density()
  
```

The distribution of r_squared is a little negatively skewed.


distribution of log

```{r}
log_result = 
 bootstrap_results %>% 
  unnest(results) %>% 
  select(.id, term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  rename(Intercept = "(Intercept)") %>% 
  mutate(log = log(Intercept*tmin))

log_result %>% 
  ggplot(aes(x = log)) + geom_density()
```

The distribution of log of estimated beta0 * estimated beta1 looks normal.



95% confidence interval

```{r}
r_squared_CI = 
  bootstrap_results %>% 
  unnest(summary) %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) %>% 
  mutate(term = "r_squared")
  
log_CI = 
  log_result %>% 
  summarize(
    ci_lower = quantile(log, 0.025), 
    ci_upper = quantile(log, 0.975)) %>% 
  mutate(term = "log(beta0*beta1)")

rbind(r_squared_CI, log_CI) %>% relocate(term) %>% 
  knitr::kable(digits = 3)
```

